State of the Practice for Lattice Boltzmann Method Software

### 2023-07-31 StateOfPractice/Papers/LatticeBoltz_SOP/LatticeBoltz_SOP.tex
Fixed additional typos for published version

Filtering by scope, usage, and age decreased the size of the list to 23
packages. We removed 22 packages for the following reasons: we cannot install
them, they are incomplete, source code is not publicly available, we are not
licensed to use them, or the project is out of scope. \citet{Michalski2021}
lists the eliminated software packages. Of the remaining 23 packages, we kept
some despite their `dead` status because of their presence on authoritative LBM
software lists and because of their surface excellence. After the initial
measurement exercise, which took place in mid-2020, we added one more package in
January 2022: Musubi. We found Musubi after our initial search, but we felt
obliged to include it since it clearly fits our criteria. Time constraints meant
we could not update the previous manual data collection, but we did redo the
automated data collection.

@@

In Table~\ref{Tbl_Guidelines}, each row corresponds to an artifact.  For a given
row, a checkmark in one of the columns means that the corresponding guideline
recommends this artifact.  The last column shows whether the artifact appears in
the measured set of LBM software, either not at all (blank), commonly (C),
uncommonly (U) or rarely (R).  We did our best to interpret the meaning of each
artifact consistently between guidelines and specific MI software, but the
terminology and the contents of artifacts are not standardized.  This challenge
even exists for the ubiquitous README file.  As illustrated by
\citet{PranaEtAl2018}, the content of README files shows significant variation
between projects.  Although some content is reasonably consistent, with 97\% of
README files containing at least one section describing the `What` of the
repository and 88.5 \% offering some `How` content, other categories are more
variable.  For instance, information on `Contribution`, `Why`, and `Who`,
appear in 27.8\%, 25.7\% and 52.9\% of the analyzed files, respectively
\citep{PranaEtAl2018}.

>>>>

Filtering by scope, usage, and age decreased the size of the list to 23
packages. We removed 22 packages for the following reasons: we cannot install
them, they are incomplete, source code is not publicly available, we are not
licensed to use them, or the project is out of scope. \citet{Michalski2021}
lists the eliminated software packages. Of the remaining 23 packages, we kept
some despite their `dead' status because of their presence on authoritative LBM
software lists and because of their surface excellence. After the initial
measurement exercise, which took place in mid-2020, we added one more package in
January 2022: Musubi. We found Musubi after our initial search, but we felt
obliged to include it since it clearly fits our criteria. Time constraints meant
we could not update the previous manual data collection, but we did redo the
automated data collection.

@@

In Table~\ref{Tbl_Guidelines}, each row corresponds to an artifact.  For a given
row, a checkmark in one of the columns means that the corresponding guideline
recommends this artifact.  The last column shows whether the artifact appears in
the measured set of LBM software, either not at all (blank), commonly (C),
uncommonly (U) or rarely (R).  We did our best to interpret the meaning of each
artifact consistently between guidelines and specific MI software, but the
terminology and the contents of artifacts are not standardized.  This challenge
even exists for the ubiquitous README file.  As illustrated by
\citet{PranaEtAl2018}, the content of README files shows significant variation
between projects.  Although some content is reasonably consistent, with 97\% of
README files containing at least one section describing the `What' of the
repository and 88.5 \% offering some `How' content, other categories are more
variable.  For instance, information on `Contribution', `Why', and `Who',
appear in 27.8\%, 25.7\% and 52.9\% of the analyzed files, respectively
\citep{PranaEtAl2018}.
